Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-10 analysis/report/effectiveness_report.Rmd
add cumulative incidence currves to markdown report

cat("  \n\n")
print(glue("### SARS-CoV-2 test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("test")
print(glue("#### Cox"), "  \n")
print_plots_effects("test", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("test", "plr")

cat("  \n\n")
print(glue("### SARS-CoV-2 positive test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("postest")
print(glue("#### Cox"), "  \n")
print_plots_effects("postest", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("postest", "plr")

cat("  \n\n")
print(glue("### A&E attendance"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("emergency")
print(glue("#### Cox"), "  \n")
print_plots_effects("emergency", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("emergency", "plr")

cat("  \n\n")
print(glue("### COVID-19 hospital admission"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("covidadmitted")
print(glue("#### Cox"), "  \n")
print_plots_effects("covidadmitted", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("covidadmitted", "plr")

>>>>

print_plots_cmlinc <- function(outcome, spline){

  calendar_curve <- read_rds(here("output", "models", outcome, "calendar", glue("reportplr_cmlinccurves_{spline}.rds"))) %>%
    mutate(timescale = "Calendar time")
  timesincevax_curve <- read_rds(here("output", "models", outcome, "timesincevax", glue("reportplr_cmlinccurves_{spline}.rds"))) %>%
    mutate(timescale = "Vaccinated time")

  curves <- bind_rows(calendar_curve, timesincevax_curve)

  plot_cmlinc <-
    ggplot(curves %>% filter(model=="3"))+
    geom_step(aes(x=tstop, y=1-survival, group=vax1_az_descr, colour=vax1_az_descr))+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0)
    )+
    scale_colour_brewer(type="qual", palette="Set2")+
    labs(
      x="Days since first dose",
      y="Cumulative risk",
      colour=NULL
    )+
    theme_bw()+
    theme(
      legend.position=c(0.05,.95),
      legend.justification = c(0,1),
      axis.text.x.top=element_text(hjust=0),

      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

    )+
    NULL

  print(plot_cmlinc)
  cat("  \n\n")
}

cat("  \n\n")
print(glue("### SARS-CoV-2 test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("test")
print(glue("#### Cox"), "  \n")
print_plots_effects("test", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("test", "plr")
print_plots_cmlinc("test", "ns")

cat("  \n\n")
print(glue("### SARS-CoV-2 positive test"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("postest")
print(glue("#### Cox"), "  \n")
print_plots_effects("postest", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("postest", "plr")
print_plots_cmlinc("postest", "ns")

cat("  \n\n")
print(glue("### A&E attendance"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("emergency")
print(glue("#### Cox"), "  \n")
print_plots_effects("emergency", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("emergency", "plr")
print_plots_cmlinc("emergency", "ns")

cat("  \n\n")
print(glue("### COVID-19 hospital admission"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("covidadmitted")
print(glue("#### Cox"), "  \n")
print_plots_effects("covidadmitted", "cox")
print(glue("#### PLR"), "  \n")
print_plots_effects("covidadmitted", "plr")
print_plots_cmlinc("covidadmitted", "ns")
